Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-10 article/article.Rmd
repository cleanup, added old word docs.

However, both of these situations are changing. Usage of online social
networking sites and other social media continues to grow, and contains social
connection and preference data for  millions of individuals. On the econometric
front, the spatial econometrics literature in the last twenty-plus years
[@Anselin2003; @Anselin2011] enables the view of spatial interaction as
a special case of social interaction, or as a proxy that may be more easily
observed in data.

@@

  1. Naturally Occurring:  Facebook data is naturally occurring when downloaded
directly from Facebook (i.e. not subject to a respondent recollection ability) 
  2. Whole Networks: Facebook.com contains complete network data of a
sociocentric nature, as opposed to an egocentric nature, which reflects the
interconnectedness of network members
  3. Longitudinal Data: Facebook data may reflect how relationships grow and
change over time; 
  4. Cultural Insight: Facebook users can indicate tastes and values, which may
be reflected in the data 
  5. Relationship Strength: Facebook can provide data on relationship strength.

@@

@@

@@

Facebook locational data (i.e., hometown and current city location) is not
geocoded, and therefore required some post-processing prior to any analyses.
Facebook location data were post-processed using R statistical programming
language and ArcGIS 10.  The study analyzed respondents’ friends who do not
consider Atlanta, Georgia as their hometown. Friends’ hometown cities were
geocoded as point locations. To associate cities as within (or outside of) the
Atlanta metropolitan region, circular buffers were created (using
Hartsfield-Jackson Atlanta International airport as the centroid) at 25 mile
radius increments from 25 miles to 150 miles. The 6 resulting hometown buffer
regions were then associated with the geocoded city locations, and thus the
number of friends with hometown city locations within each buffer region were
determined. Only data from respondents that completed the entire survey (i.e.
the air travel diary, socio-demographic section, and the Facebook data
collection) were considered for the analysis.

>>>>

However, both of these situations are changing. Usage of online social
networking sites and other social media continues to grow, and contains social
connection and preference data for  millions of individuals. On the econometric
front, the spatial econometrics literature in the last twenty-plus years
[@Anselin2003; @Anselin2011] enables the view of spatial interaction as
a special case of social interaction, or as a proxy that may be more easily
observed in data. In other words, the spatial relationships that many authors
have observed are often substitutes for implied social relationships.

@@

  1. Naturally Occurring:  Facebook data is naturally occurring when downloaded
directly from Facebook (i.e. not subject to a respondent recollection ability) 
  2. Whole Networks: Facebook contains complete network data of a
sociocentric nature, as opposed to an egocentric nature, which reflects the
interconnectedness of network members
  3. Longitudinal Data: Facebook data may reflect how relationships grow and
change over time; 
  4. Cultural Insight: Facebook users can indicate tastes and values, which may
be reflected in the data 
  5. Relationship Strength: Facebook can provide data on relationship strength.

@@

Tie Strength
---------------------------------------

@@

```{r number_trips}
#calculate number of user trips
number_trips <- trips %>%
  group_by(id) %>%
  summarise(number_trips = n())

user <- user %>%
  left_join(number_trips)
```

@@

***discussion of why we care about how far friends are from Atlanta***

```{r distance_from_atlanta}
cities <- read.csv("data/PRIVATEDATA/geocode/geocoded_datatables/allcities.csv")%>%
  tbl_df()
